Integrated approach to modeling to krill population dynamics in Wester Antarctic Peninsula: spatial and ecosystem considerations

### 2024-06-05 index.Rmd
test model to example

```{r message=FALSE, warning=FALSE}
dir01 <- here("s01") # agreggate data (no spatial diferences)
dir1<-here("s1") # Data strata flishery
dir2<-here("s2") # Same 9 with areas (SubStrata) as fleet. Dif size comoposition and dif CPUE and dif survey length and biomass data by strata
dir3<-here("s3") # whitout S-R
dir4<-here("s4") # 
dir5<-here("s5") # whitout S-R
dir6<-here("s6") # whitout S-R
dir7<-here("s7") # whitout S-R
dir8<-here("s8")
Figs <- here("Figs")# S2 set parametres EMM-2024/23 (Mardones)
```

@@

```{r}
# leo archivos para plotear y hacer tablas
start2 <- SS_readstarter(file = file.path(dir2,
                                          "starter.ss"),
                              verbose = FALSE)
# note the data and control file names can vary, so are determined from the 
# starter file.
dat2 <- SS_readdat(file = file.path(dir2, start2$datfile),
                        verbose = FALSE)
# Read in ctl file. Note that the data fileR object is needed so that SS_readctl
# assumes the correct data structure
ctl2 <-  r4ss::SS_readctl(file = file.path(dir2,
                                    start2$ctlfil),
                        verbose = FALSE,
                        use_datlist = TRUE, 
                   datlist = dat2)
fore2 <- r4ss::SS_readforecast(file = file.path(dir2, 
                                                "forecast.ss"),
                              verbose = FALSE)
# can also read in wtatage.ss for an empirical wt at age model using
# r4ss::SS_readwtatage()
```

```{r}
parbio<-ctl2$MG_parms[1:10,c(1:3,7)]
 row.names( parbio)<-c("Nat M",
                       "Lmin", 
                       "Lmax",
                       "VonBert K",
                       "CV young",
                       "CV old", 
                       "Wt a", 
                       "Wt b",
                       "L50%", 
                       "Mat slope")

 SRpar<-ctl2$SR_parms[1:5,c(1:3,7)]
 Qpar<-ctl2$Q_parms[1:2,c(1:3,7)]
 Selpar<-ctl2$size_selex_parms[1:22,c(1:3,7)]
 parInit<-rbind(parbio,SRpar,Qpar,Selpar)

@@

| Scenario | Description                                                                          |
|:------------:|:---------------------------------------------------------|
|   s01    | Fishery and Survey (AMLR) data, Predator, Environmental aggregate data in 48.1       |
|    s1    | Fishery data (Length, Index, Catch) by strata and Predator and Env data              |
|    s2    | Fishery and Survey (AMLR) data Length, Index, Catch by strata. Predator and Env data |
|    s3    | "s2" without S-R relation                                                            |
|    s4    | "s2" Ricker S-R relation estimated                                                   |
|    s5    | "s2" BH S-R relation weak (0.9 steepness)                                            |
|    s6    | "s2" BH S-R relation strong (0.6 steepness)                                          |
|    s7    | "s2" BH S-R relation mid-strong (0.65 steepness) estimated                           |
|    s8    | "s2" w/ set of parameters estimated in @EMM-204/32                                   |

@@

```{r eval=FALSE, message=F, include=FALSE}
# Lista de directorios para correro tordos juntos
directorios <- c("s01", 
                 "s1", 
                 "s2",
                 "s3",
                 "s4",
                 "s5",
                 "s6",
                 "s7",
                 "s8")  # Agrega aquí todos los nombres de las carpetas que deseas procesar

@@

```{r eval=FALSE, message=F, include=FALSE}
#OR with rby separate
#shell(cmd="ss") # run SS to windows
# or 
#system('./ss_osx') # to mac
r4ss::run(
  dir = dir01,
  exe = "ss_osx",
  skipfinished = FALSE, # TRUE will skip running if Report.sso present
  show_in_console = TRUE # change to true to watch the output go past
)
```

@@

#s7
base.model8 <- SS_output(dir=dir8,
                        covar=T,
                        forecast=T)
```

```{r eval=FALSE, message=F, include=FALSE}
SS_plots(base.model3, 
         uncertainty = TRUE,
         datplot = T, 
         png=T, 
         aalresids = F,
         btarg=0.75, 
         minbthresh=0.2, 
         forecast=T)
```

@@

SSplotData(base.model2, 
           subplot = 1,
           pheight = 15)

@@

```{r}
SSplotSelex(base.model2,
            subplots = 1)
```
```{r}
SSplotComps(base.model01)
SSplotComps(base.model1)
SSplotComps(base.model2)
SSplotComps(base.model3)
SSplotComps(base.model4)
SSplotComps(base.model5)
SSplotComps(base.model6)
SSplotComps(base.model7)
SSplotComps(base.model8)

# RESULTS

@@

## Residual consistency in `s2`

```{r eval=FALSE}
SSplotRunstest(base.model2, 
               subplots = "cpue",
               add=T)
```

```{r}
SSplotJABBAres(base.model01,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model1,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model2,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model3,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model4,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model5,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model6,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model7,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model7,
               subplots = "len",
               add=T)

SSplotMnwt(base.model01, subplots = 2)
```

@@

```{r eval=FALSE}
l <- base.model4$recruit$SpawnBio
m <- base.model4$recruit$pred_recr
ggplot()+
  aes(l,m)+
  geom_point()+
  geom_smooth(method = "lm", 
              se =F)+
  ylim(0, max(base.model2$recruit$pred_recr))
```

@@

@@

retroSummary7 <- SSsummarize(retroModels7)

#s8
retroModels8 <- SSgetoutput(dirvec=file.path(dir8,
                                            "Retrospective",
                                            paste("retro",0:-5,
                                                  sep="")))

retroSummary8 <- SSsummarize(retroModels8)

@@

```{r echo FALSE}
#save(retroSummary, retroModels, file="retro5.Rdata")

@@

retro7 <- SSplotRetro(retroSummary7,
            add=T,
            forecast = F,
            legend = T,
            verbose=F)
retro8 <- SSplotRetro(retroSummary8,
            add=T,
            forecast = F,
            legend = T,
            verbose=F)

@@

@@

```{r}
hci = SSplotHCxval(retroSummary2, 
                   add = T, 
                   verbose = F, 
                   legendcex = 0.7)
```

@@

mvln = SSdeltaMVLN(base.model8,
                   Fref = "Btgt", 
                   plot = TRUE,
                   addprj=TRUE,
                   virgin = TRUE,
                   mc=100)

@@

```{r echo=FALSE}
# model01
tablebias01 <- SShcbias(retroSummary01,quant="SSB",verbose=F)
tablebias02 <- SShcbias(retroSummary01,quant="F",verbose=F)

@@

kbl(tablebias02, booktabs = T,format = "latex",
    caption = "Rho parameter in F model s01")  %>% 
    kable_styling(latex_options = "HOLD_position")

# model2
tablebias7 <- SShcbias(retroSummary7,quant="SSB",verbose=F)
tablebias07 <- SShcbias(retroSummary7,quant="F",verbose=F)

kbl(tablebias7, booktabs = T,format = "latex",
    caption = "Rho parameter in SSB model s2")  %>% 
    kable_styling(latex_options = "HOLD_position")

kbl(tablebias7, booktabs = T,format = "latex",
    caption = "Rho parameter in F model s2")  %>% 
    kable_styling(latex_options = "HOLD_position")
```

@@

```{r}
like01 <- base.model01$likelihoods_used
like01$model <- rep("s01", nrow(like01))
like01 <- rownames_to_column(like01, var = "Description")
like1 <- base.model1$likelihoods_used
like1$model <- rep("s1", nrow(like1))
like1 <- rownames_to_column(like1, var = "Description")
like2 <- base.model1$likelihoods_used
like2$model <- rep("s2", nrow(like2))
like2 <- rownames_to_column(like2, var = "Description")
like3 <- base.model3$likelihoods_used
like3$model <- rep("s3", nrow(like3))
like3 <- rownames_to_column(like3, var = "Description")
like4 <- base.model4$likelihoods_used
like4$model <- rep("s4", nrow(like4))
like4 <- rownames_to_column(like4, var = "Description")
like5 <- base.model5$likelihoods_used
like5$model <- rep("s5", nrow(like5))
like5 <- rownames_to_column(like5, var = "Description")
like6 <- base.model6$likelihoods_used
like6$model <- rep("s6", nrow(like6))
like6 <- rownames_to_column(like6, var = "Description")
like7 <- base.model7$likelihoods_used
like7$model <- rep("s7", nrow(like7))
like7 <- rownames_to_column(like7, var = "Description")
like8 <- base.model8$likelihoods_used
like8$model <- rep("s8", nrow(like8))
like8 <- rownames_to_column(like8, var = "Description")
totalike <- rbind(like01,
                  like1,
                   like2,
                   like3,
                   like4,
                   like5,
                   like6,
                   like7,
                  like8)

@@

```{r}
ggplot(totalike)+
  geom_bar( aes(y = reorder(Description, values), x =values),
            stat = "identity", position = "dodge") +
  theme_few() +
  facet_wrap(.~model, 
             ncol=3)+
  labs(y="",
       x="Likelihood")+
  theme(axis.text.x = element_text(angle = 90, 
                                   hjust = 1)) 
```

@@

dirname.model.run <- here("s2")

@@

?SS_profile()

@@

@@

@@

              ymax=150,minfraction = 0.001,

@@

@@

```{r}
outps2 <- base.model2$timeseries[1:53, 2:8]

addWorksheet(wb, "variable_s2")
writeData(wb, "variable_s2", outps2)

@@

```{r echo=FALSE}
#PLOT labels, name of each model run
legend.labels <- c( "s01",
                  "s1",
                 "s2",
                 "s3",
                 "s4",
                 "s5",
                 "s6",
                 "s7",
                 "s8")

#read in all model runs
#note if cover=T you need a hessian; if covar=F you do not need a hessian
biglist <- SSgetoutput(keyvec = NULL,
                       dirvec = c(dir01,
                                  dir1,
                                  dir2,
                                  dir3,
                                  dir4,
                                  dir5,
                                  dir6,
                                  dir7,
                                  dir8),
                       getcovar = F)

#create summary of model runs from list above
summaryoutput <- SSsummarize(biglist)

SSplotComparisons(summaryoutput,
                  legendlabels = c("No Spatial",
                                   "s1",
                                   "s2",
                 "s3",
                 "s4",
                 "s5",
                 "s6",
                 "s7",
                 "s8"),
                 labels = c("Year", 
                            "Spawning biomass (t)",
                            "Relative spawning biomass", 
                            "Age-0 recruits (1,000s)",
                            "Recruitment deviations", 
                            "Index", "Log index", 
                            "1 - SPR", 
                            "Density",
                            "Management target", 
                            "Minimum stock size threshold",
                            "Spawning output",
                            "Harvest rate"),
                 png=TRUE,plotdir=Figs)

@@

```{r}
comtable <- SStableComparisons(summaryoutput,
                   likenames = c("TOTAL", 
                                 "Survey", 
                                 "Length_comp",
                                 "Age_comp", 
                                 "priors",
                                 "Size_at_age"), 
                   names = c("Recr_Virgin",
                             "R0", 
                             "steep",
                             "NatM",
                             "L_at_Amax", 
                             "VonBert_K", 
                             "SSB_Virg", 
                             "Bratio_2017",
                             "SPRratio_2016"),
                   digits = NULL,
                   modelnames = c("s01", "s1","s2",
                 "s3",
                 "s4",
                 "s5",
                 "s6",
                 "s7"),
                   csv = FALSE,
                   csvdir =~"/DOCAS/SA_Krill",
                   csvfile = "parameter_comparison_table.csv",
                 verbose = TRUE,
                   mcmc = FALSE)
kbl(comtable, booktabs = T,format = "latex",
    caption = "Comparacion likelihood y parámetros s01, s1, s2, s3, s4, s5, s6 y s7")  %>% 
    kable_styling(latex_options = "scale_down")

@@

comparision between select models

```{r echo=FALSE}
#read in all model runs
#note if cover=T you need a hessian; if covar=F you do not need a hessian
biglist <- SSgetoutput(keyvec = NULL,
                       dirvec = c(
                                  dir8,

                                  dir2,
                                  dir3),
                       getcovar = F)

#create summary of model runs from list above
summaryoutput <- SSsummarize(biglist)

SSplotComparisons(summaryoutput,
                  legendlabels = c(
                                   "s8",

>>>>

```{r message=FALSE, warning=FALSE}
dir01 <- here("s01") # agreggate data (no spatial diferences)
dir1<-here("s1") # Data strata flishery
dir2<-here("s2") # Same 9 with areas (SubStrata) as fleet. Dif size comoposition and dif CPUE and dif survey length and biomass data by strata
dir3<-here("s3") # whitout S-R
dir4<-here("s4") # 
dir5<-here("s5") # whitout S-R
dir6<-here("s6") # whitout S-R
dir7<-here("s7") # whitout S-R
dirtest<-here("test")
Figs <- here("Figs")# S2 set parametres EMM-2024/23 (Mardones)
```

@@

```{r}
# leo archivos para plotear y hacer tablas
start1 <- SS_readstarter(file = file.path(dir1,
                                          "starter.ss"),
                              verbose = FALSE)
# note the data and control file names can vary, so are determined from the 
# starter file.
dat1 <- SS_readdat(file = file.path(dir1, start1$datfile),
                        verbose = FALSE)
# Read in ctl file. Note that the data fileR object is needed so that SS_readctl
# assumes the correct data structure
ctl1 <-  r4ss::SS_readctl(file = file.path(dir1,
                                    start1$ctlfil),
                        verbose = FALSE,
                        use_datlist = TRUE, 
                   datlist = dat1)
fore1 <- r4ss::SS_readforecast(file = file.path(dir1, 
                                                "forecast.ss"),
                              verbose = FALSE)
# can also read in wtatage.ss for an empirical wt at age model using
# r4ss::SS_readwtatage()
```

```{r}
parbio<-ctl1$MG_parms[1:10,c(1:3,7)]
 row.names( parbio)<-c("Nat M",
                       "Lmin", 
                       "Lmax",
                       "VonBert K",
                       "CV young",
                       "CV old", 
                       "Wt a", 
                       "Wt b",
                       "L50%", 
                       "Mat slope")

 SRpar<-ctl1$SR_parms[1:5,c(1:3,7)]
 Qpar<-ctl1$Q_parms[1:2,c(1:3,7)]
 Selpar<-ctl1$size_selex_parms[1:22,c(1:3,7)]
 parInit<-as.data.frame(rbind(parbio,SRpar,Qpar,Selpar))

@@

| Scenario | Description                                                                          |
|:------------:|:---------------------------------------------------------|
|   s01    | Fishery and Survey (AMLR) data, Predator, Environmental aggregate data in 48.1       |
|    s1    | Fishery and Survey (AMLR) data Length, Index, Catch by strata. Predator and Env data |
|    s2    | "s1" without S-R relation                                                            |
|    s3    | "s1" BH S-R relation weak (0.9 steepness)                                            |
|    s4    | "s1" BH S-R relation strong (0.6 steepness)                                          |
|    s5    | "s1" BH S-R relation mid-strong estimated                                            |
|    s6    | "s1" Ricker S-R relation estimated                                                   |
|    s7    | "s1" w/ set of parameters estimated in @EMM-204/32                                   |

@@

```{r eval=FALSE, message=F, include=FALSE}
# Lista de directorios para correro tordos juntos
directorios <- c("s01", 
                 "s1", 
                 "s2",
                 "s3",
                 "s4",
                 "s5",
                 "s6",
                 "s7")  # Agrega aquí todos los nombres de las carpetas que deseas procesar

@@

```{r eval=FALSE, message=F, include=FALSE}
#OR with rby separate
#shell(cmd="ss") # run SS to windows
# or 
r4ss::run(
  dir = dir7,
  exe = "ss_osx",
  skipfinished = FALSE, # TRUE will skip running if Report.sso present
  show_in_console = TRUE # change to true to watch the output go past
)
```

@@

```
# RESULTS

### Main Variables poulation

Total biomass

```{r}
total01 <- as.data.frame(base.model01$timeseries[1:50,c(2,5)]) %>%
  mutate(Serie = "No Spatial")
total1 <- as.data.frame(base.model1$timeseries[,c(2,5)]) %>% 
  mutate(Serie = "Spatial implicit")
total2 <- as.data.frame(base.model2$timeseries[,c(2,5)]) %>% 
  mutate(Serie = "Spatial w/ without S-R relation")
total3 <- as.data.frame(base.model3$timeseries[,c(2,5)]) %>% 
  mutate(Serie = "Spatial w/ S-R relation weak (0.9 steepness)")
total4 <- as.data.frame(base.model4$timeseries[,c(2,5)]) %>% 
  mutate(Serie = "Spatial w/ S-R relation strong (0.6 steepness)")
total5 <- as.data.frame(base.model5$timeseries[,c(2,5)]) %>% 
  mutate(Serie = "Spatial w/ S-R relation mid-strong estimated ")
total6 <- as.data.frame(base.model6$timeseries[,c(2,5)]) %>% 
  mutate(Serie = "Spatial w/ Ricker S-R relation estimated")
total7 <- as.data.frame(base.model7$timeseries[,c(2,5)]) %>% 
  mutate(Serie = "Spatial w/ New set parameters Linf, k and M")

totalbio <- rbind(total01,
              total1,
              total2,
              total3,
              total4,
              total5,
              total6,
              total7)

ggplot(totalbio, aes(x = Yr, y = Bio_all, color=Serie)) +
  geom_point(size=0.7,
             col="black") +
  geom_smooth(method = "loess",
              span=0.75, 
              se=TRUE)+
  labs(title = "Compare variables between scenarios",
       x = "",
       y = "Total biomass (mt)") +
  theme_few() +
  scale_color_viridis_d(option="H",
                        name="Scenarios")+
  theme(axis.text.x = element_text(angle = 90,
                                   hjust = 1))
```

```{r eval=FALSE, message=F, include=FALSE}
SS_plots(base.model7, 
         uncertainty = TRUE,
         datplot = T, 
         png=T, 
         aalresids = F,
         btarg=0.75, 
         minbthresh=0.2, 
         forecast=T)
```

Data used en both (spatial and No spatial models)

@@

SSplotData(base.model1, 
           subplot = 1,
           pheight = 15)
```

@@

```{r}
SSplotSelex(base.model01,
            subplots = 1)
SSplotSelex(base.model1,
            subplots = 1)
SSplotSelex(base.model2,
            subplots = 1)
SSplotSelex(base.model3,
            subplots = 1)
SSplotSelex(base.model4,
            subplots = 1)
SSplotSelex(base.model5,
            subplots = 1)
SSplotSelex(base.model6,
            subplots = 1)
SSplotSelex(base.model7,
            subplots = 1)
```

```{r eval=FALSE}
SSplotComps(base.model01,
            subplots = 1,
            maxrows = 5,
            maxcols = 5)

SSplotComps(base.model1,
            subplots = 1,
            maxrows = 5,
            maxcols = 5)
SSplotComps(base.model2,
            subplots = 1,
            maxrows = 5,
            maxcols = 5)
SSplotComps(base.model3,
            subplots = 1,
            maxrows = 5,
            maxcols = 5)
SSplotComps(base.model4,
            subplots = 1,
            maxrows = 5,
            maxcols = 5)
SSplotComps(base.model5,
            subplots = 1,
            maxrows = 5,
            maxcols = 5)
SSplotComps(base.model6,
            subplots = 1,
            maxrows = 5,
            maxcols = 5)
SSplotComps(base.model7,
            subplots = 1,
            maxrows = 5,
            maxcols = 5)
```

@@

## Residual consistency 
```{r}
SSplotRunstest(base.model01,
               subplots = "len",
               add=T)
SSplotRunstest(base.model1,
               subplots = "len",
               add=T)
SSplotRunstest(base.model2,
               subplots = "len",
               add=T)
SSplotRunstest(base.model3,
               subplots = "len",
               add=T)
SSplotRunstest(base.model4,
               subplots = "len",
               add=T)
SSplotRunstest(base.model5,
               subplots = "len",
               add=T)
SSplotRunstest(base.model6,
               subplots = "len",
               add=T)
SSplotRunstest(base.model7,
               subplots = "len",
               add=T)
```

```{r}
SSplotRunstest(base.model01,
               subplots = "cpue",
               add=T)
SSplotRunstest(base.model1,
               subplots = "cpue",
               add=T)
SSplotRunstest(base.model2,
               subplots = "cpue",
               add=T)
SSplotRunstest(base.model3,
               subplots = "cpue",
               add=T)
SSplotRunstest(base.model4,
               subplots = "cpue",
               add=T)
SSplotRunstest(base.model5,
               subplots = "cpue",
               add=T)
SSplotRunstest(base.model6,
               subplots = "cpue",
               add=T)
SSplotRunstest(base.model7,
               subplots = "cpue",
               add=T)
```

```{r eval=FALSE}
SSplotJABBAres(base.model01,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model1,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model2,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model3,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model4,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model5,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model6,
               subplots = "len",
               add=T)
SSplotJABBAres(base.model7,
               subplots = "len",
               add=T)
```

```{r}
SSplotJABBAres(base.model01,
               subplots = "cpue",
               add=T)
SSplotJABBAres(base.model1,
               subplots = "cpue",
               add=T)
SSplotJABBAres(base.model2,
               subplots = "cpue",
               add=T)
SSplotJABBAres(base.model3,
               subplots = "cpue",
               add=T)
SSplotJABBAres(base.model4,
               subplots = "cpue",
               add=T)
SSplotJABBAres(base.model5,
               subplots = "cpue",
               add=T)
SSplotJABBAres(base.model6,
               subplots = "cpue",
               add=T)
SSplotJABBAres(base.model7,
               subplots = "cpue",
               add=T)
```

@@

```{r eval=FALSE}
l <- base.model1$recruit$SpawnBio
m <- base.model1$recruit$pred_recr
ggplot()+
  aes(l,m)+
  geom_point()+
  geom_smooth(method = "loess", 
              se =F)+
  theme_few()+
  ylim(0, max(base.model1$recruit$pred_recr))
```

@@

```{r eval=FALSE}
#one by one
retro(
    dir = dir1,
    oldsubdir = "",
    newsubdir = "Retrospective",
    years = 0:-5,
    exe = "ss_osx",
    extras = "-nox",
    skipfinished = FALSE)
```

@@

retroSummary7 <- SSsummarize(retroModels7)
```

```{r eval=FALSE, message=FALSE, warning=FALSE}
#stest
retroModelstest <- SSgetoutput(dirvec=file.path(dirtest,
                                            "Retrospective",
                                            paste("retro",0:-3,
                                                  sep="")))

retroSummary <- SSsummarize(retroModelstest)

@@

```{r echo=FALSE}
#save(retroSummary, retroModels, file="retro5.Rdata")

@@

retro7 <- SSplotRetro(retroSummary7,
            add=T,
            forecast = F,
            legend = T,
            verbose=F)

@@

```{r eval=FALSE}
retrotest <- SSplotRetro(retroSummarytest,
            add=T,
            forecast = F,
            legend = T,
            verbose=F)
```

@@

```{r}
hci = SSplotHCxval(retroSummary01, 
                   add = T, 
                   verbose = F, 
                   legendcex = 0.7)
hci = SSplotHCxval(retroSummary1, 
                   add = T, 
                   verbose = F, 
                   legendcex = 0.7)
hci = SSplotHCxval(retroSummary2, 
                   add = T, 
                   verbose = F, 
                   legendcex = 0.7)
hci = SSplotHCxval(retroSummary3, 
                   add = T, 
                   verbose = F, 
                   legendcex = 0.7) 
hci = SSplotHCxval(retroSummary4, 
                   add = T, 
                   verbose = F, 
                   legendcex = 0.7)
hci = SSplotHCxval(retroSummary5, 
                   add = T, 
                   verbose = F, 
                   legendcex = 0.7)
hci = SSplotHCxval(retroSummary6, 
                   add = T, 
                   verbose = F, 
                   legendcex = 0.7)
hci = SSplotHCxval(retroSummary7, 
                   add = T, 
                   verbose = F, 
                   legendcex = 0.7)
```

@@

@@

another

```{r eval=FALSE}

nanios<-base.model1$Kobe$Yr
SSBDep<-base.model1$Kobe$B.Bmsy
y_BDPR<-base.model1$Kobe$F.Fmsy

# Integrated Model

kobe1 <- ggplot(base.model1$Kobe)+
  #geom_line(aes(kobebro$BBMSY, kobebro$FFMSY)) +
  geom_rect(aes(xmin = 0, xmax = 0.5, ymin = 0, ymax = 5),
            fill = "#E43338", alpha = 0.5) +
  geom_rect(aes(xmin = 0.5, xmax = 0.75, ymin = 0, ymax = 5),
            fill = "#F2ED23", alpha = 0.5) +
  geom_rect(aes(xmin = 0.75, xmax = 1.25, ymin = 0, ymax = 5),
            fill = "#ACC39A", alpha = 0.5) +
  geom_rect(aes(xmin = 1.25, xmax = 9, ymin = 0, ymax = 1),
            fill = "#608D68", alpha = 0.5) +
  geom_rect(aes(xmin = 1.25, xmax = 9, ymin = 1, ymax = 5),
            fill = "#808080", alpha = 0.5) +
  geom_path(aes(x=base.model1$Kobe$B.Bmsy,y=base.model1$Kobe$F.Fmsy,label=base.model1$Kobe$Yr))+
  geom_point(aes(base.model1$Kobe$B.Bmsy, base.model1$Kobe$F.Fmsy),
             lwd=2) +
  geom_hline(yintercept = 1) +
  geom_vline(xintercept = c(0.5, 0.75, 1.75, 1, 1.25), linetype=2)+
  theme_few()+
  labs(x = expression("BD/BD"[RMS]), y = expression("F/F"[RMS]))+
  # geom_text(data = texto_coords, aes(x = x, y = y, label = etiqueta),
  #            vjust = -0.5)+
  geom_text(aes(x=base.model1$Kobe$B.Bmsy,y=base.model1$Kobe$F.Fmsy,label=base.model1$Kobe$Yr),
            nudge_y = 0.1,size = 3,
            check_overlap = TRUE)
kobe1

```{r echo=FALSE}
# model01
tablebias01 <- SShcbias(retroSummary01,quant="SSB",verbose=F)
tablebias01a <- SShcbias(retroSummary01,quant="F",verbose=F)

@@

kbl(tablebias01a, booktabs = T,format = "latex",
    caption = "Rho parameter in F model s01")  %>% 
    kable_styling(latex_options = "HOLD_position")

# model1
tablebias1 <- SShcbias(retroSummary1,quant="SSB",verbose=F)
tablebias1a <- SShcbias(retroSummary1,quant="F",verbose=F)

kbl(tablebias1, booktabs = T,format = "latex",
    caption = "Rho parameter in SSB model s1")  %>% 
    kable_styling(latex_options = "HOLD_position")

kbl(tablebias1a, booktabs = T,format = "latex",
    caption = "Rho parameter in F model s1")  %>% 
    kable_styling(latex_options = "HOLD_position")

# model2
tablebias2 <- SShcbias(retroSummary2,quant="SSB",verbose=F)
tablebias2a <- SShcbias(retroSummary2,quant="F",verbose=F)

kbl(tablebias2, booktabs = T,format = "latex",
    caption = "Rho parameter in SSB model s2")  %>% 
    kable_styling(latex_options = "HOLD_position")

kbl(tablebias2a, booktabs = T,format = "latex",
    caption = "Rho parameter in F model s2")  %>% 
    kable_styling(latex_options = "HOLD_position")

# model3
tablebias3 <- SShcbias(retroSummary3,quant="SSB",verbose=F)
tablebias3a <- SShcbias(retroSummary3,quant="F",verbose=F)

kbl(tablebias3, booktabs = T,format = "latex",
    caption = "Rho parameter in SSB model s3")  %>% 
    kable_styling(latex_options = "HOLD_position")

kbl(tablebias3a, booktabs = T,format = "latex",
    caption = "Rho parameter in F model s3")  %>% 
    kable_styling(latex_options = "HOLD_position")

# model4
tablebias4 <- SShcbias(retroSummary4,quant="SSB",verbose=F)
tablebias4a <- SShcbias(retroSummary4,quant="F",verbose=F)

kbl(tablebias4, booktabs = T,format = "latex",
    caption = "Rho parameter in SSB model s4")  %>% 
    kable_styling(latex_options = "HOLD_position")

kbl(tablebias4a, booktabs = T,format = "latex",
    caption = "Rho parameter in F model s4")  %>% 
    kable_styling(latex_options = "HOLD_position")

# model5
tablebias5 <- SShcbias(retroSummary5,quant="SSB",verbose=F)
tablebias5a <- SShcbias(retroSummary5,quant="F",verbose=F)

kbl(tablebias5, booktabs = T,format = "latex",
    caption = "Rho parameter in SSB model s5")  %>% 
    kable_styling(latex_options = "HOLD_position")

kbl(tablebias5a, booktabs = T,format = "latex",
    caption = "Rho parameter in F model s5")  %>% 
    kable_styling(latex_options = "HOLD_position")

# model6
tablebias6 <- SShcbias(retroSummary6,quant="SSB",verbose=F)
tablebias6a <- SShcbias(retroSummary6,quant="F",verbose=F)

kbl(tablebias6, booktabs = T,format = "latex",
    caption = "Rho parameter in SSB model s6")  %>% 
    kable_styling(latex_options = "HOLD_position")

kbl(tablebias6a, booktabs = T,format = "latex",
    caption = "Rho parameter in F model s6")  %>% 
    kable_styling(latex_options = "HOLD_position")

# model7
tablebias7 <- SShcbias(retroSummary7,quant="SSB",verbose=F)
tablebias7a <- SShcbias(retroSummary7,quant="F",verbose=F)

kbl(tablebias7, booktabs = T,format = "latex",
    caption = "Rho parameter in SSB model s7")  %>% 
    kable_styling(latex_options = "HOLD_position")

kbl(tablebias7a, booktabs = T,format = "latex",
    caption = "Rho parameter in F model s7")  %>% 
    kable_styling(latex_options = "HOLD_position")

@@

```{r}
like01 <- base.model01$likelihoods_used
like01$model <- rep("s01", nrow(like01))
like01 <- rownames_to_column(like01, var = "Description")
like1 <- base.model1$likelihoods_used
like1$model <- rep("s1", nrow(like1))
like1 <- rownames_to_column(like1, var = "Description")
like2 <- base.model1$likelihoods_used
like2$model <- rep("s2", nrow(like2))
like2 <- rownames_to_column(like2, var = "Description")
like3 <- base.model3$likelihoods_used
like3$model <- rep("s3", nrow(like3))
like3 <- rownames_to_column(like3, var = "Description")
like4 <- base.model4$likelihoods_used
like4$model <- rep("s4", nrow(like4))
like4 <- rownames_to_column(like4, var = "Description")
like5 <- base.model5$likelihoods_used
like5$model <- rep("s5", nrow(like5))
like5 <- rownames_to_column(like5, var = "Description")
like6 <- base.model6$likelihoods_used
like6$model <- rep("s6", nrow(like6))
like6 <- rownames_to_column(like6, var = "Description")
like7 <- base.model7$likelihoods_used
like7$model <- rep("s7", nrow(like7))
like7 <- rownames_to_column(like7, var = "Description")

totalike <- rbind(like01,
                  like1,
                   like2,
                   like3,
                   like4,
                   like5,
                   like6,
                   like7)

@@

```{r}
ggplot(totalike)+
  geom_bar( aes(y = reorder(Description, values), x =log(values)),
            stat = "identity", position = "dodge") +
  theme_few() +
  facet_wrap(.~model, 
             ncol=4)+
  labs(y="",
       x="Log Likelihood")+
  theme(axis.text.x = element_text(angle = 90, 
                                   hjust = 1))+
  xlim(0,20)
```

@@

dirname.model.run <- here("s1")

@@

#?SS_profile()

@@

                                 "Catch",

@@

                                 "Catch Likelihood",

@@

              ymax=2050,minfraction = 0.001,

@@

## Convergence criteria

0.0001 final convergence criteria (e.g. 1.0e-04)

@@

```{r}
outps1 <- base.model1$timeseries[1:53, 2:8]

addWorksheet(wb, "variable_s2")
writeData(wb, "variable_s2", outps1)

@@

```{r echo=FALSE}

#read in all model runs
#note if cover=T you need a hessian; if covar=F you do not need a hessian
biglist <- SSgetoutput(keyvec = NULL,
                       dirvec = c(dir01,
                                  dir1,
                                  dir2,
                                  dir3,
                                  dir4,
                                  dir5,
                                  dir6,
                                  dir7),
                       getcovar = F)

#create summary of model runs from list above
summaryoutputall <- SSsummarize(biglist)
```

```{r echo=FALSE}
compall <- SSplotComparisons(summaryoutputall,
                  legendlabels = c("No Spatial",
                                   "s1",
                                   "s2",
                 "s3",
                 "s4",
                 "s5",
                 "s6",
                 "s7"),
                 labels = c("Year", 
                            "Spawning biomass (t)",
                            "Relative spawning biomass", 
                            "Age-0 recruits (1,000s)",
                            "Recruitment deviations", 
                            "Index", "Log index", 
                            "1 - SPR", 
                            "Density",
                            "Management target", 
                            "Minimum stock size threshold",
                            "Spawning output",
                            "Harvest rate"),
                 png=TRUE,plotdir=Figs)

@@

```{r}
comtable <- SStableComparisons(summaryoutputall,
                   likenames = c("TOTAL", 
                                 "Survey", 
                                 "Length_comp",
                                 "Age_comp", 
                                 "priors",
                                 "Size_at_age"), 
                   names = c("Recr_Virgin",
                             "R0", 
                             "steep",
                             "NatM",
                             "L_at_Amax", 
                             "VonBert_K", 
                             "SSB_Virg", 
                             "Bratio_2020",
                             "SPRratio_2020"),
                   digits = NULL,
                   modelnames = c("s01", "s1","s2",
                 "s3",
                 "s4",
                 "s5",
                 "s6",
                 "s7"),
                   csv = F,
                   csvdir =~"/DOCAS/SA_Krill",
                   csvfile = "parameter_comparison_table.csv",
                 verbose = TRUE,
                   mcmc = FALSE)
kbl(comtable, booktabs = T,format = "latex",
    caption = "Comparacion likelihood y parámetros s01, s1, s2, s3, s4, s5, s6 y s7")  %>% 
    kable_styling(latex_options = "scale_down")

@@

comparision between select models `No spatial`and `Spatial implicit` and `Spatial W/ new set parametres`

```{r echo=FALSE}
#read in all model runs
#note if cover=T you need a hessian; if covar=F you do not need a hessian
biglist01_1_7 <- SSgetoutput(keyvec = NULL,
                       dirvec = c(
                                  dir01,
                                  dir1,
                                  dir7),
                       getcovar = F)

#create summary of model runs from list above
summaryoutput01_1_7 <- SSsummarize(biglist01_1_7)

comp01_1_7 <- SSplotComparisons(summaryoutput01_1_7,
                  legendlabels = c(
                                   "No Spatial",

                 "Spatial",
                 "Spatial w/ new set LH paramters"),
                 labels = c("Year", 
                            "Spawning biomass (t)",
                            "Relative spawning biomass", 
                            "Age-0 recruits (1,000s)",
                            "Recruitment deviations", 
                            "Index", "Log index", 
                            "1 - SPR", 
                            "Density",
                            "Management target", 
                            "Minimum stock size threshold",
                            "Spawning output",
                            "Harvest rate"),
                 png=TRUE,plotdir=Figs)
```

comparision between select models `Old Paramters` and `New Parameters WG SAM 2024/23`
